---
title: "Analysis on networks: Gender patterns in Parliamentary Speech - doi: 10.1332/251510821X1653948960862"
author: "Klara Raiber"
date: "18/05/2022"
---

#setup
```{r setup}
library(dplyr)
library(stringr)
library(plyr)
library(foreign)
library(tidyr)
library(kableExtra)
library(caret)
library(plotmo)
library(PRROC)
library(verification)
library(beepr)
library(dplyr)
library(haven)
library(tidyverse)
library(magrittr)
library(plotly)
library(ggplot2)
library(quanteda)
library(readtext)
library(antiword)
library(XML)
library(httr)
library(methods)
library(data.table)
library(tidytext)
library(NLP)
library(tm)
library(igraph)
#library(regexSelect)
library(mclust)
library(tictoc)
#library(RSQLite)
library(digest)
#install.packages("reshape")
library(reshape)

## Clear and working directory

setwd("") # insert own file directory


#clear environment
rm(list=ls())

#set seed
set.seed(2109)

#check memory limit
memory.limit()
memory.limit(size = 20000)
```

# Building co-occurrence matrices

#females

```{r}
#sub-corpus
load("corp_wom.Rda")
#feature co-occurrence matrix
wom_fcm <- fcm(corp_wom, context = 'window', 
               window = 7)
#save co-occurrence matrix
save(wom_fcm, file="wom_fcm.Rda")

```

#male

```{r}
#sub-coprus
load("corp_men.Rda")
#feature co-occurrence matrix
men_fcm <- fcm(corp_men, context = 'window', 
               window = 7)
#save co-occurrence matrix
save(men_fcm, file="men_fcm.Rda")

```

#Built semantic networks

```{r}
#################
#####FEMALES#####
#################
load("wom_fcm.Rda")


#Built Igraph network
adj_wom <- fcm_select(wom_fcm, valuetype = 'fixed')
wom_graph <- graph_from_adjacency_matrix(adj_wom, weighted = NULL,
                                         mode = c("undirected"), diag = FALSE)

#save
save(wom_graph, file="wom_graph.Rda")

load("wom_graph.Rda")
#check edge density
edge_density(wom_graph, loops=F) #0.002311603

#diameter is the length of the longest path (in number of edges) between two nodes
diameter(wom_graph, directed=FALSE, weights=NA) #5

#mean_distance is the average number of edges between any two nodes in the network.
mean_distance(wom_graph, directed=FALSE) #2.574375

wom_graph$damen
#################
######MALES######
#################
load("men_fcm.Rda")


adj_men <- fcm_select(men_fcm, valuetype = 'fixed')
men_graph <- graph_from_adjacency_matrix(adj_men, weighted = NULL,
                                         mode = c("undirected"), diag = FALSE)

#save
save(men_graph, file="men_graph.Rda")

load("men_graph.Rda")
#check edge density
edge_density(men_graph, loops=F) #0.002061899

#diameter is the length of the longest path (in number of edges) between two nodes
tic()
diameter(men_graph, directed=FALSE, weights=NA) #4
toc()

#mean_distance is the average number of edges between any two nodes in the network.
mean_distance(men_graph, directed=FALSE) #2.570824



```

#Check if damen there to belittle 
```{r}
load("wom_fcm.Rda")
load("men_fcm.Rda")
pattern_damen <- c("damen", "herren", "ruhe", "beruhigen", "kollegen", "kolleginnen")
wom_d_h_combis <- fcm_select(wom_fcm, pattern = pattern_damen) # 5214 times damen and herren said together

men_d_h_combis <- fcm_select(men_fcm, pattern = pattern_damen) # 10358 times damen and herren said tigether

load("wom_full.Rda")
#5277 times damen, 5238 times herren

load("men_full.Rda")
#10521 times damen, 10386 times herren



```

#plots
#females

#German 
```{r}
load("wom_fcm.Rda")
feat_wom_G <- names(topfeatures(wom_fcm, 50)) #topfeatures() returns the most frequently co-occurring words
fcmat_wom_50_G <- fcm_select(wom_fcm, pattern = feat_wom_G)


fcmat_wom_50_G@Dimnames <-
  list(
    features = c(
      "Kolleginnen",
      "Kollegen",
      "vielen",
      "ja",
      "müssen",
      "Dank",
      "Frau",
      "Bundesregierung",
      "möchte",
      "Präsidentin",
      "immer",
      "Deutschland",
      "unsere",
      "Menschen",
      "Land",
      "wirklich",
      "viele",
      "natürlich",
      "Euro",
      "Jahr",
      "leben",
      "brauchen",
      "Kollege",
      "wurde",
      "Linke",
      "Drucksache",
      "Bündnis",
      "stimmen",
      "Ausschuss",
      "wer",
      "unserem",
      "stimmt",
      "dagegen",
      "beschlossen",
      "Beratung",
      "enthält",
      "endlich",
      "glaube",
      "Gesetz",
      "Frauen",
      "Kinder",
      "Kommunen",
      "Gesetzentwurf",
      "Milliarden",
      "Millionen",
      "darf",
      "diejenigen",
      "angenommen",
      "Flüchtlinge",
      "Beschlussempfehlung"
    ),
    features =  c(
      "Kolleginnen",
      "Kollegen",
      "vielen",
      "ja",
      "müssen",
      "Dank",
      "Frau",
      "Bundesregierung",
      "möchte",
      "Präsidentin",
      "immer",
      "Deutschland",
      "unsere",
      "Menschen",
      "Land",
      "wirklich",
      "viele",
      "natürlich",
      "Euro",
      "Jahr",
      "leben",
      "brauchen",
      "Kollege",
      "wurde",
      "Linke",
      "Drucksache",
      "Bündnis",
      "stimmen",
      "Ausschuss",
      "wer",
      "unserem",
      "stimmt",
      "dagegen",
      "beschlossen",
      "Beratung",
      "enthält",
      "endlich",
      "glaube",
      "Gesetz",
      "Frauen",
      "Kinder",
      "Kommunen",
      "Gesetzentwurf",
      "Milliarden",
      "Millionen",
      "darf",
      "diejenigen",
      "angenommen",
      "Flüchtlinge",
      "Beschlussempfehlung"
    )
  )

#size <- log(colSums(dfm_select(wom_fcm, feat_wom_G)))
#ploi_wom_G <- textplot_network(fcmat_wom_50_G, min_freq = 0.8, 
 #                              vertex_size = size / max(size)* 3, 
  #                             edge_color = "darkslategrey")



ploi_wom_G <- textplot_network(fcmat_wom_50_G, min_freq = 0.8, edge_color = "darkslategrey")
ploi_wom_G




#save
ggsave(ploi_wom_G, filename = "network_wom_German.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)
```

#English
```{r}
load("wom_fcm.Rda")
feat_wom <- names(topfeatures(wom_fcm, 50)) #topfeatures() returns the most frequently co-occurring words
feat_wom
fcmat_wom_50 <- fcm_select(wom_fcm, pattern = feat_wom)


fcmat_wom_50@Dimnames <- list(features = c("colleagues (female)", "colleagues (male)", "many [1]", "yes", "have to", "thanks", "Mrs./women",  "government", "want", "president (female)",  "always", "Germany", "our [1]", "people", "country", "really", "many [2]", "natural", "euro", "year", "live",  "need", "colleague (male)", "was", "left",  "official documents", "alliance", "vote [1]", "committee","who", "our [2]", "vote [2]", "dissent", "decided", "consultation", "abstain", "finally", "believe", "act", "women", "children", "municipalities", "bill", "billions", "millions", "allowed", "those", "adopted", "refugees", 
"recom. resolution"), 
                              features =  c("colleagues (female)", "colleagues (male)", "many [1]", "yes", "have to", "thanks", "Mrs./women",  "government", "want", "president (female)",  "always", "Germany", "our [1]", "people", "country", "really", "many [2]", "natural", "euro", "year", "live",  "need", "colleague (male)", "was", "left",  "official documents", "alliance", "vote [1]", "committee","who", "our [2]", "vote [2]", "dissent", "decided", "consultation", "abstain", "finally", "believe", "act", "women", "children", "municipalities", "bill", "billions", "millions", "allowed", "those", "adopted", "refugees", 
"recom. resolution"))



#size <- log(colSums(dfm_select(wom_fcm, feat_wom)))
ploi1 <- textplot_network(fcmat_wom_50, min_freq = 0.8,
                          edge_color = "darkslategrey")
ploi1



#save
ggsave(ploi1, filename = "network_wom_eng_20201012.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)
```

#males

#German
```{r}
load("men_fcm.Rda")
feat_men <- names(topfeatures(men_fcm, 50)) #topfeatures() returns the most frequntly co-occuring words
fcmat_men_50_G <- fcm_select(men_fcm, pattern = feat_men)


fcmat_men_50_G@Dimnames <-
  list(
    features = c(
      "Kollegen",
      "müssen",
      "gibt",
      "Menschen",
      "immer",
      "dafür",
      "Euro",
      "sagen",
      "liebe",
      "gut",
      "tun",
      "Kolleginnen",
      "ja",
      "Kollege",
      "Präsident",
      "möchte",
      "stellen",
      "deutlich",
      "letzten",
      "darauf",
      "gerade",
      "Bundesregierung",
      "deswegen",
      "natürlich",
      "wichtig",
      "Union",
      "Antrag",
      "Grünen",
      "wurde",
      "sage",
      "darum",
      "Kollegin",
      "wäre",
      "reden",
      "gar",
      "Recht",
      "Jahr",
      "glaube",
      "Millionen",
      "Thema",
      "gesagt",
      "Geld",
      "Beispiel",
      "Gesetz",
      "richtig",
      "Vizepräsidentin",
      "Bund",
      "Gesetzentwurf",
      "Kommunen",
      "zahlen"
    ),
    features =  c(
      "Kollegen",
      "müssen",
      "gibt",
      "Menschen",
      "immer",
      "dafür",
      "Euro",
      "sagen",
      "liebe",
      "gut",
      "tun",
      "Kolleginnen",
      "ja",
      "Kollege",
      "Präsident",
      "möchte",
      "stellen",
      "deutlich",
      "letzten",
      "darauf",
      "gerade",
      "Bundesregierung",
      "deswegen",
      "natürlich",
      "wichtig",
      "Union",
      "Antrag",
      "Grünen",
      "wurde",
      "sage",
      "darum",
      "Kollegin",
      "wäre",
      "reden",
      "gar",
      "Recht",
      "Jahr",
      "glaube",
      "Millionen",
      "Thema",
      "gesagt",
      "Geld",
      "Beispiel",
      "Gesetz",
      "richtig",
      "Vizepräsidentin",
      "Bund",
      "Gesetzentwurf",
      "Kommunen",
      "zahlen"
    )
  )


ploi_men_G <- textplot_network(fcmat_men_50_G, min_freq = 0.8, 
                          edge_color = "darkslategrey")
ploi_men_G 
#save
ggsave(ploi_men_G, filename = "ploi_men_G.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm"
       , dpi = 500)
```

#English
```{r}
load("men_fcm.Rda")
feat_men <- names(topfeatures(men_fcm, 50)) #topfeatures() returns the most frequntly co-occuring words
feat_men
fcmat_men_50 <- fcm_select(men_fcm, pattern = feat_men)

fcmat_men_50@Dimnames <-
  list(
    features = c(
      "colleagues (male)",
      "have to",
      "give",
      "people",
      "always",
      "in favor",
      "euro",
      "saying [1]",
      "dear",
      "good",
      "doing",
      "colleagues (female)",
      "yes",
      "colleague (male)",
      "president (male)",
      "want",
      "provide",
      "clear",
      "last",
      "then",
      "just",
      "government",
      "therefore [1]",
      "natural",
      "important",
      "union",
      "request",
      "greens",
      "was",
      "saying [2]",
      "therefore [2]",
      "colleague (female)",
      "would be",
      "talking",
      "even",
      "law",
      "year",
      "believe",
      "millions",
      "topic",
      "said",
      "money",
      "example",
      "act",
      "correct",
      "vice-president (female)",
      "federation",
      "bill",
      "municipalities",
      "paying"
    ),
    features =  c(
      "colleagues (male)",
      "have to",
      "give",
      "people",
      "always",
      "in favor",
      "euro",
      "saying [1]",
      "dear",
      "good",
      "doing",
      "colleagues (female)",
      "yes",
      "colleague (male)",
      "president (male)",
      "want",
      "provide",
      "clear",
      "last",
      "then",
      "just",
      "government",
      "therefore [1]",
      "natural",
      "important",
      "union",
      "request",
      "greens",
      "was",
      "saying [2]",
      "therefore [2]",
      "colleague (female)",
      "would be",
      "talking",
      "even",
      "law",
      "year",
      "believe",
      "millions",
      "topic",
      "said",
      "money",
      "example",
      "act",
      "correct",
      "vice-president (female)",
      "federation",
      "bill",
      "municipalities",
      "paying"
    )
  )



ploi2 <- textplot_network(fcmat_men_50, min_freq = 0.8,  
                          edge_color = "darkslategrey")
ploi2 

#save
ggsave(ploi2, filename = "ploi_men_eng_20201012.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm"
       , dpi = 500)
```

#Key words - hub centrality scores - with addressing

```{r}
#################
#####FEMALES#####
#################

load("wom_graph.Rda")

#hub centrality
hub_wom <- as.data.frame(hub_score(wom_graph))
#include words in data frame
hub_wom$words <- rownames(hub_wom)y

#rearange order
hub_wom <- hub_wom[order(-hub_wom$vector),]
#select 15 most important keywords
hub_wom_15 <- hub_wom[1:15,]

#################
######MALES######
#################

load("men_graph.Rda")

#hub centrality
hub_men <- as.data.frame(hub_score(men_graph))
#include words in data frame
hub_men$words <- rownames(hub_men)

#rearange order
hub_men <- hub_men[order(-hub_men$vector),]
#select 15 most important keywords
hub_men_15 <- hub_men[1:15,]

```

##excluding forms of adressing _oa

```{r}
#pattern to delete
address <-
  c(
    "liebe",
    "kollegen",
    "kolleginnen",
    "sehr",
    "geehrte",
    "damen",
    "herren",
    "vielen",
    "dank"
  )

#################
#####FEMALES#####
#################
load("wom_fcm.Rda")
wom_fcm_oa <- fcm_remove(wom_fcm, pattern = address)
save(wom_fcm_oa, file="wom_fcm_oad.Rda")

#network
adj_wom_oa <- fcm_select(wom_fcm_oa, valuetype = 'fixed')
wom_graph_oa <- graph_from_adjacency_matrix(adj_wom_oa, weighted = NULL,
                                            mode = c("undirected"), diag = FALSE)
save(wom_graph_oa, file="wom_graph_oad.Rda")


#################
######MALES######
#################
load("men_fcm.Rda")
men_fcm_oa <- fcm_remove(men_fcm, pattern = address)
save(men_fcm_oa, file="men_fcm_oad.Rda")

#network
adj_men_oa <- fcm_select(men_fcm_oa, valuetype = 'fixed')
men_graph_oa <- graph_from_adjacency_matrix(adj_men_oa, weighted = NULL,
                                            mode = c("undirected"), diag = FALSE)
save(men_graph_oa, file="men_graph_oad.Rda")

```

#key words - hub scores - without addressing _oa

```{r}
#################
#####FEMALES#####
#################

load("wom_graph_oad.Rda")
#simplify 

#hub centrality
hub_wom_oa <- as.data.frame(hub_score(wom_graph_oa))
#include words in data frame
hub_wom_oa$words <- rownames(hub_wom_oa)

#rearange order
hub_wom_oa <- hub_wom_oa[order(-hub_wom_oa$vector),]
#select 15 most important keywords
hub_wom_oa_15 <- hub_wom_oa[1:15,]

hub_wom_oa_15$words

#################
######MALES######
#################


load("men_graph_oad.Rda")

#hub centrality
hub_men_oa <- as.data.frame(hub_score(men_graph_oa))
#include words in data frame
hub_men_oa$words <- rownames(hub_men_oa)

#rearange order
hub_men_oa <- hub_men_oa[order(-hub_men_oa$vector),]
#select 15 most important keywords
hub_men_oa_15 <- hub_men_oa[1:15,]
hub_men_oa_15$words

####################
#######GRAPHS#######
####################

#################
#####FEMALES#####
#################


#include translation
hub_wom_oa_15$labels <-
  c(
    "wer (who)",
    "stimmt (vote*)",
    "Beschlussempfehlung (recom.
                          resolution)",
    "Drucksache (official documents)",
    "dagegen (dissent)",
    "Fraktion (parliamentary group)",
    "Gr?nen (greens)",
    "stimmen (vote*)",
    "enth?lt (abstain)",
    "B?ndnis (alliance)",
    "Linke (left)",
    "Gesetzentwurf (bill)",
    "Beratung (consultation)",
    "Antrag (request)",
    "angenommen (adopted)"
  )


write.xlsx(hub_wom_oa_15$labels, file = "translation.xlsx", append)

#Hubs females
graph_hub_wom <- ggplot(hub_wom_oa_15, aes(x=reorder(labels, vector), y=vector)) +
  theme_set(theme_classic()) +
  theme(axis.text.y = element_text(size = 10)) +
  geom_bar(stat="identity", width = 0.7, fill = "darkgrey",
           position=position_dodge()) +
  coord_flip() + 
  labs(x = "Words", y = "Hub centrality", 
       title ="Women")


graph_hub_wom  
ggsave(graph_hub_wom, filename = "wom_hub.jpg", device = "jpg", width = 10, height = 14, units = "cm", dpi = 500)

#################
######MALES######
#################


#include translation
hub_men_oa_15$labels <-
  c(
    "müssen (have to)",
    "mehr (more)",
    "Deutschland (Germany)",
    "Menschen (people)",
    "schon (already)",
    "gibt (give*)",
    "sagen (saying)",
    "Euro (euro)",
    "geht (go*)",
    "heute (today)",
    "Herr (Mr.)",
    "ganz (completely)",
    "dafür (in favor)",
    "immer (always)",
    "Frage (question)"
  )


#hubs males
graph_hub_men <- ggplot(hub_men_oa_15, aes(x=reorder(labels, vector), y=vector)) +
  theme_set(theme_classic()) +
  theme(axis.text.y = element_text(size = 10)) +            
  geom_bar(stat="identity", width = 0.7, fill =  "darkslategrey",
           position=position_dodge()) +
  coord_flip() + 
  labs(x = "Words", y = "Hub centrality", 
       title ="Men")


graph_hub_men  
ggsave(graph_hub_men, filename = "men_hub.jpg", device = "jpg", width = 9, height = 14, units = "cm",dpi = 500)
```


#exclude female vice presidents _ovp

```{r}
#Ulla Schmidt (11002019)
#Edelgard Bulmahn (11000305)
#Petra Pau (11003206)
#Claudia Roth (11003212)

load("wom_fcm.Rda")
load("corp_wom.Rda")
#IDs of vice presidents
ID_vp <- c("11002019", "11000305", "11003206","11003212")

#exclude vice presidents from female corpus
corp_wom_ovp <- corpus_subset(corp_wom, ID!=ID_vp)

#feature co-occurrence matrix
wom_fcm_ovp <- fcm(corp_wom_ovp, context = 'window', 
                   window = 7)

#save
save(wom_fcm_ovp, file="wom_fcm_ovp.Rda")

#Built Igraph network
adj_wom_ovp <- fcm_select(wom_fcm_ovp, valuetype = 'fixed')
wom_graph_ovp <- graph_from_adjacency_matrix(adj_wom_ovp, weighted = NULL,
                                             mode = c("undirected"), diag = FALSE)


#save
save(wom_graph_ovp, file="wom_graph_ovp.Rda")
```

#exclude female vice presidents _ovp also Michaela Noll

```{r}
#Ulla Schmidt (11002019)
#Edelgard Bulmahn (11000305)
#Petra Pau (11003206)
#Claudia Roth (11003212)

load("wom_fcm.Rda")
load("corp_wom.Rda")
#IDs of vice presidents
ID_vp <- c("11002019", "11000305", "11003206","11003212", "11003645")

#exclude vice presidents from female corpus
corp_wom_ovp <- corpus_subset(corp_wom, ID!=ID_vp)

#feature co-occurrence matrix
wom_fcm_ovp_noll <- fcm(corp_wom_ovp, context = 'window', 
                   window = 7)

#save
save(wom_fcm_ovp_noll, file="wom_fcm_ovp_noll.Rda")

#Built Igraph network
adj_wom_ovp <- fcm_select(wom_fcm_ovp_noll, valuetype = 'fixed')
wom_graph_ovp_noll <- graph_from_adjacency_matrix(adj_wom_ovp, weighted = NULL,
                                             mode = c("undirected"), diag = FALSE)


#save
save(wom_graph_ovp_noll, file="wom_graph_ovp_noll.Rda")
```

#plot without vice presidents _ovp

```{r}
load("wom_fcm_ovp.Rda")
#plot on female network
feat_wom_ovp <- names(topfeatures(wom_fcm_ovp, 50)) #topfeatures() returns the most frequntly co-occuring words<
fcmat_wom_50_ovp <- fcm_select(wom_fcm_ovp, pattern = feat_wom_ovp)

#fcmat_wom_50_ovp@Dimnames
fcmat_wom_50_ovp@Dimnames <-
  list(
    features = c(
      "Kolleginnen",
      "Kollegen",
      "vielen",
      "ja",
      "müssen",
      "Dank",
      "Frau",
      "Bundesregierung",
      "möchte",
      "Präsidentin",
      "immer",
      "Deutschland",
      "unsere",
      "Menschen",
      "Land",
      "wirklich",
      "viele" ,
      "natürlich",
      "Euro",
      "Jahr",
      "deswegen",
      "Geld",
      "leben",
      "brauchen",
      "Kollege",
      "wurde",
      "Linke",
      "Drucksache",
      "Bündnis",
      "Ausschuss",
      "gar",
      "wer",
      "unserem",
      "stimmt",
      "dagegen",
      "Beratung",
      "bereits",
      "endlich",
      "glaube",
      "Gesetz",
      "Frauen",
      "Kinder",
      "Kommunen",
      "Gesetzentwurf",
      "Milliarden",
      "millionen",
      "darf",
      "Flüchtlinge",
      "angenommen",
      "Beschlussempfehlung"
    ),
    features =  c(
      "Kolleginnen",
      "Kollegen",
      "vielen",
      "ja",
      "müssen",
      "Dank",
      "Frau",
      "Bundesregierung",
      "möchte",
      "Präsidentin",
      "immer",
      "Deutschland",
      "unsere",
      "Menschen",
      "Land",
      "wirklich",
      "viele" ,
      "natürlich",
      "Euro",
      "Jahr",
      "deswegen",
      "Geld",
      "leben",
      "brauchen",
      "Kollege",
      "wurde",
      "Linke",
      "Drucksache",
      "Bündnis",
      "Ausschuss",
      "gar",
      "wer",
      "unserem",
      "stimmt",
      "dagegen",
      "Beratung",
      "bereits",
      "endlich",
      "glaube",
      "Gesetz",
      "Frauen",
      "Kinder",
      "Kommunen",
      "Gesetzentwurf",
      "Milliarden",
      "millionen",
      "darf",
      "Flüchtlinge",
      "angenommen",
      "Beschlussempfehlung"
    )
  )


graph_wom_ovp <- textplot_network(fcmat_wom_50_ovp, min_freq = 0.8, 
                                  edge_color = "darkslategrey")
graph_wom_ovp


#save
ggsave(graph_wom_ovp, filename = "ploi_wom_ovp.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)

```

#plot without vice presidents _ovp without Michaela Noll

```{r}
load("wom_fcm_ovp_noll.Rda")
#plot on female network
feat_wom_ovp <- names(topfeatures(wom_fcm_ovp_noll, 50)) #topfeatures() returns the most frequntly co-occuring words
fcmat_wom_50_ovp <- fcm_select(wom_fcm_ovp_noll, pattern = feat_wom_ovp)

graph_wom_ovp_noll <- textplot_network(fcmat_wom_50_ovp, min_freq = 0.8, 
                                  edge_color = "darkslategrey")
graph_wom_ovp_noll


#save
ggsave(graph_wom_ovp_noll, filename = "ploi_wom_ovp_noll.jpg",
       device = "jpg", width = 20 , height = 14,
       units = "cm", dpi = 500)

```

#keywords without vice presidents with addressing _ovp

```{r}

#load
load("wom_graph_ovp.Rda")


#hub centrality
hub_wom_ovp <- as.data.frame(hub_score(wom_graph_ovp))
#include words in data frame
hub_wom_ovp$words <- rownames(hub_wom_ovp)

#rearange order
hub_wom_ovp <- hub_wom_ovp[order(-hub_wom_ovp$vector),]
#select 15 most important keywords
hub_wom_ovp_25 <- hub_wom_ovp[1:25,]

####################
#######GRAPHS#######
####################



hub_wom_ovp_25$labels <-
  c(
    "Kollegen (male: colleagues)",
    "Kolleginnen (female: colleagues)",
    "liebe (dear)",
    "Frau (woman/Mrs.)",
    "Herr (Mr.)",
    "Präsidentin (female: president)",
    "vielen (very)",
    "Dank (thanks)",
    "mehr (more)",
    "müssen (have to)",
    "Damen (ladies)",
    "Menschen (people)",
    "Herren (gentlemen)",
    "schon (already)",
    "wer (who)",
    "heute (today)",
    "gibt (give*)",
    "ganz (completely)",
    "geehrte (dear)",
    "Grüne (greens)",
    "Fraktion (parliamentary group)",
    "sagen (saying)",
    "immer (always)",
    "geht (go*)",
    "ja (yes)"
  )



#grpah on hubs without female vice presidents
graph_hub_wom_ovp <- ggplot(hub_wom_ovp_25, aes(x=reorder(labels, vector), y=vector)) +
  theme_set(theme_classic()) +
  theme(axis.text.y = element_text(size = 10)) +
  geom_bar(stat="identity", width = 0.7, fill =  "darkgrey",
           position=position_dodge()) +
  coord_flip() + 
  labs(x = "Words", y = "Hub centrality", 
       title ="Women without vice presidents")


graph_hub_wom_ovp
ggsave(graph_hub_wom_ovp, filename = "graph_hub_ovp.jpg", device = "jpg", width = 14, height = 20, units = "cm", dpi = 500)

```
#keywords without vice presidents with addressing _ovp without Michaela Noll

```{r}

#load
load("wom_graph_ovp_noll.Rda")


#hub centrality
hub_wom_ovp <- as.data.frame(hub_score(wom_graph_ovp_noll))
#include words in data frame
hub_wom_ovp$words <- rownames(hub_wom_ovp)

#rearange order
hub_wom_ovp <- hub_wom_ovp[order(-hub_wom_ovp$vector),]
#select 15 most important keywords
hub_wom_ovp_25 <- hub_wom_ovp[1:25,]

```

#keywords without vice presidents without addressing _oa_ovp

```{r}
#pattern to delete
address <-
  c("liebe",
    "kollegen",
    "kolleginnen",
    "sehr",
    "geehrte",
    "damen",
    "herren",
    "vielen",
    "dank"
  )

#################
#####FEMALES#####
#################
load("wom_fcm_ovp.Rda")
wom_fcm_oa_ovp <- fcm_remove(wom_fcm_ovp, pattern = address)
save(wom_fcm_oa_ovp, file="wom_fcm_oa_ovp.Rda")

#network
adj_wom_oa_ovp <- fcm_select(wom_fcm_oa_ovp, valuetype = 'fixed')
wom_graph_oa_ovp <- graph_from_adjacency_matrix(adj_wom_oa_ovp, weighted = NULL,
                                                mode = c("undirected"), diag = FALSE)
save(wom_graph_oa_ovp, file="wom_fcm_oa_ovp.Rda")



#hub centrality
hub_wom_oa_ovp <- as.data.frame(hub_score(wom_graph_oa_ovp))
#include words in data frame
hub_wom_oa_ovp$words <- rownames(hub_wom_oa_ovp)

#rearange order
hub_wom_oa_ovp <- hub_wom_oa_ovp[order(-hub_wom_oa_ovp$vector),]
#select 15 most important keywords
hub_wom_oa_ovp_15 <- hub_wom_oa_ovp[1:15,]


####################
#######GRAPHS#######
####################
hub_wom_oa_ovp_15$labels <-
  c(
    "wer (who)",
    "stimmt (vote*)",
    "mehr (more)",
    "müssen (have to)",
    "Menschen (people)",
    "schon (already)",
    "Fraktion (parliamentary group)",
    "Grünen (greens)",
    "Drucksache (official documents)",
    "gibt (give*)",
    "Beschlusssache (recommended resolution)",
    "dagegen (dissent)",
    "Gesetzentwurf (bill)",
    "ganz (completely)",
    "dafür (in favor)"
  )



#hubs males
graph_hub_ovp_oa <- ggplot(hub_wom_oa_ovp_15, aes(x=reorder(labels, vector),
                                                  y=vector)) +
  theme_set(theme_classic()) +
  theme(axis.text.y = element_text(size = 10)) +
  geom_bar(stat="identity", width = 0.7, fill = "darkgrey",
           position=position_dodge()) +
  coord_flip() + 
  labs(x = "Words", y = "Hub centrality", 
       title ="Women without vice presidents")


graph_hub_ovp_oa

ggsave(graph_hub_ovp_oa, filename = "graph_hub_ovp_oa.jpg", device = "jpg", width = 18, height = 14, units = "cm", dpi = 500)




```
#keywords without vice presidents without addressing _oa_ovp without Michaela Noll

```{r}
#pattern to delete
address <-
  c(
    "liebe",
    "kollegen",
    "kolleginnen",
    "sehr",
    "geehrte",
    "damen",
    "herren",
    "vielen",
    "dank"
  )

#################
#####FEMALES#####
#################
load("wom_fcm_ovp_noll.Rda")
wom_fcm_oa_ovp_noll <- fcm_remove(wom_fcm_ovp_noll, pattern = address)
save(wom_fcm_oa_ovp_noll, file="wom_fcm_oa_ovp_noll.Rda")

#network
adj_wom_oa_ovp <- fcm_select(wom_fcm_oa_ovp_noll, valuetype = 'fixed')
wom_graph_oa_ovp_noll <- graph_from_adjacency_matrix(adj_wom_oa_ovp, weighted = NULL,
                                                mode = c("undirected"), diag = FALSE)
save(wom_graph_oa_ovp_noll, file="wom_fcm_oa_ovp_noll.Rda")



#hub centrality
hub_wom_oa_ovp <- as.data.frame(hub_score(wom_graph_oa_ovp_noll))
#include words in data frame
hub_wom_oa_ovp$words <- rownames(hub_wom_oa_ovp)

#rearange order
hub_wom_oa_ovp <- hub_wom_oa_ovp[order(-hub_wom_oa_ovp$vector),]
#select 15 most important keywords
hub_wom_oa_ovp_15 <- hub_wom_oa_ovp[1:15,]





```

##calculate hub centralities for all female politicians

```{r eval=false}
load("Stammdaten18.Rda")
#################
#####FEMALES#####
#################
load("wom_fcm.Rda")

#to get only ID of females
total_wom <- subset(total18, GESCHLECHT=="weiblich")

load("corp_wom.Rda")
IDs <- unique(corp_wom$documents$ID)

load("dtm_wom.Rda")


#put individual data to data frame in a loop
q <- corpus_subset(corp_wom, (ID==IDs[1])) # subset corpus for ID
p <- fcm(q, context = 'window', window = 7)
w <- fcm_select(p, valuetype = 'fixed')
o <- graph_from_adjacency_matrix(w, weighted = NULL,
                                 mode = c("undirected"), diag = FALSE)
hub <- as.data.frame(hub_score(o))
hub_full <- hub[c(1)]
names(hub_full)[1] <- IDs[1]
hub_wom_i <- transpose(hub_full)
#keep row and column names
colnames(hub_wom_i) <- rownames(hub_full)
rownames(hub_wom_i) <- colnames(hub_full)


for (i in c(2:length(IDs))) {
  tic()
  q <- corpus_subset(corp_wom, (ID==IDs[i])) # subset corpus for ID
  p <- fcm(q, context = 'window', window = 7)
  w <- fcm_select(p, valuetype = 'fixed')
  o <- graph_from_adjacency_matrix(w, weighted = NULL,
                                   mode = c("undirected"), diag = FALSE)
  hub <- as.data.frame(hub_score(o))
  y <- hub[c(1)]
  names(y)[1] <- IDs[i]
  hub_2 <- transpose(y)
  #keep row and column names
  colnames(hub_2) <- rownames(y)
  rownames(hub_2) <- colnames(y)
  
  hub_wom_i <- full_join(hub_wom_i, hub_2)
  
  
  
  print(i)
  toc()
}

save(hub_wom_i, file="hub_wom_i_45.Rda")


save(hub_wom_i, file="hub_wom_i.Rda")
beep("complete")


load("hub_wom_i.Rda")
head(hub_wom_i)
```

##calculate hub centralities for all male politicians

```{r eval=FALSE echo=FALSE}
load("Stammdaten18.Rda")
#################
######MALES######
#################

load("men_fcm.Rda")

#to get only ID of females
total_men <- subset(total18, GESCHLECHT=="männlich")

load("corp_men.Rda")
IDs <- unique(corp_men$documents$ID)

load("dtm_men.Rda")


#put individual data to data frame in a loop


q <- corpus_subset(corp_men, (ID==IDs[1])) # subset corpus for ID
p <- fcm(q, context = 'window', window = 7)
w <- fcm_select(p, valuetype = 'fixed')
o <- graph_from_adjacency_matrix(w, weighted = NULL,
                                 mode = c("undirected"), diag = FALSE)
hub <- as.data.frame(hub_score(o))
hub_full <- hub[c(1)]
names(hub_full)[1] <- IDs[1]
hub_men_i <- transpose(hub_full)
#keep row and column names
colnames(hub_men_i) <- rownames(hub_full)
rownames(hub_men_i) <- colnames(hub_full)


for (i in c(1:length(IDs))) {
  tic()
  q <- corpus_subset(corp_men, (ID==IDs[i])) # subset corpus for ID
  p <- fcm(q, context = 'window', window = 7)
  t <- fcm_keep(p, pattern = intersect_words)
  w <- fcm_select(t, valuetype = 'fixed')
  o <- graph_from_adjacency_matrix(w, weighted = NULL,
                                   mode = c("undirected"), diag = FALSE)
  hub <- as.data.frame(hub_score(o))
  y <- hub[c(1)]
  names(y)[1] <- IDs[i]
  hub_2 <- transpose(y)
  #keep row and column names
  colnames(hub_2) <- rownames(y)
  rownames(hub_2) <- colnames(y)
  
  hub_men_i <- full_join(hub_men_i, hub_2)
  
  
  
  print(i)
  toc()
}

#save
save(hub_men_i, file="hub_men_i_full.Rda")
#beep("complete")

##Note: I cut this loop into pieces to reduce computing time. First, 1 to 95, then 96 to 211, then 211 to the end. I joint them by using full_join.
```

## Hub centralities of individuals

```{r}
#################
#####FEMALES#####
#################
load("hub_wom_i.Rda")
head(hub_wom_i)
max(hub_wom_i$wer,na.rm = TRUE)
summary(hub_wom_i$wer,na.rm = TRUE)
table(hub_wom_i$wer) #4 people have "wer" as their keyword. Check who:

p_wer <- c("wer")
wer <- hub_wom_i[p_wer] # 3 4 5 6 
load("corp_wom.Rda")
IDs <- unique(corp_wom$documents$ID)
IDs[3:6] #  "11000305" "11002019" "11003206" "11003212"
#Ulla Schmidt (11002019)
#Edelgard Bulmahn (11000305)
#Petra Pau (11003206)
#Claudia Roth (11003212)


summary(hub_wom_i$stimmt) #no one as their 1, max. 0.89 - for full: 0.797
table(hub_wom_i$stimmt)

summary(hub_wom_i$liebe)
table(hub_wom_i$liebe) #25 have it as their 1

summary(hub_wom_i$frau)
table(hub_wom_i$frau) #6 as their 1 

summary(hub_wom_i$mehr) #mean 0.39
table(hub_wom_i$mehr) #5 as their 1

#summary(hub_wom_i$m?ssen) #mean 0.39
#table(hub_wom_i$m?ssen) # 13 as their 1

summary(hub_wom_i$menschen) #mean 0.37 
table(hub_wom_i$menschen) #23 as their 1 

summary(hub_wom_i$fraktion) #mean 0.035
table(hub_wom_i$fraktion) # max: 0.95 of one person


#################
######MALES######
#################
load("hub_men_i_full.Rda")

summary(hub_men_i_full$liebe) #mean 0.398
table(hub_men_i_full$liebe) #15

#summary(hub_men_i_full$m?ssen) #mean 0.46
#table(hub_men_i_full$m?ssen) #40

summary(hub_men_i_full$menschen) #mean 0.305
table(hub_men_i_full$menschen) #11

summary(hub_men_i_full$mehr) #0.396
table(hub_men_i_full$mehr) #12

summary(hub_men_i_full$deutschland) #0.334
table(hub_men_i_full$deutschland) #15

```

